%-------------------------
% ATS-Optimized & Realistic One-Page Resume
% Author: Priyanshu Gupta (Final Version by AI)
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Standard margins for a full, well-proportioned page
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% ATS-friendly section formatting with balanced spacing
\titleformat{\section}{
  \vspace{-4pt}\bfseries\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine readable
\pdfgentounicode=1

%-------------------------
% Custom commands with balanced spacing
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge Priyanshu Gupta} \\ \vspace{1pt}
  \small 8800295258 $|$ \href{mailto:pg0000742@gmail.com}{\underline{pg0000742@gmail.com}} $|$
  \href{https://www.linkedin.com/in/priyanshu-gupta-4ba240259}{\underline{linkedin.com/in/priyanshu-gupta-4ba240259}} $|$
  \href{https://github.com/PriyanshuGupta1102}{\underline{github.com/PriyanshuGupta1102}}
\end{center}

%-----------SUMMARY-----------
\section{Professional Summary}
  \resumeSubHeadingListStart
    \resumeItem{Full-Stack Developer with expertise in the MERN stack and automated testing. Delivered production applications with 99\% uptime while optimizing APIs to reduce response times by 40\% and cutting manual testing effort by 60\%. Skilled in API design, database management, and CI/CD.}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Guru Tegh Bahadur Institute of Technology}{New Delhi, IN}
      {Bachelor of Technology in Computer Science and Engineering}{November 2022 - Present}
      \resumeSubItem{Expected Graduation: May 2026 $|$ Current CGPA: 9.13/10}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {SFP Education and Technology Pvt Ltd}{New Delhi, IN}
      {Full Stack Web Developer Intern}{June 2024 - August 2024}
      \resumeItemListStart
        % REALISTIC CHANGE 1: "Contributed to" is more believable than "Engineered"
        \resumeItem{Contributed to key features for 2 web applications serving 500+ users, using React.js for the front-end and Node.js for the back-end.}
        % REALISTIC CHANGE 2: "Assisted in" and "contributing to" shows teamwork
        \resumeItem{Assisted in optimizing database queries and API endpoints, contributing to a 40\% reduction in average server response time (from 800ms to 480ms).}
        \resumeItem{Participated in an Agile team of 6 developers, engaging in daily stand-ups and code reviews to deliver features 15\% ahead of sprint deadlines.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Technical Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{AI Wrapper Project \quad $|$ \quad Streamlit, Python, OpenAI API, Pandas, Numpy, Plotly}{October 2025}
\resumeItemListStart
    \resumeItem{Developed a modular AI-driven platform combining financial tools, news aggregation, and generative AI to assist with investment decisions.}
    \resumeItem{Integrated a growth projection module to predict investment outcomes based on user-defined parameters like initial amount, time horizon, and expected return.}
    \resumeItem{Implemented AI-backed portfolio analysis, offering personalized insights on diversification, asset allocation, and risk management.}
    \resumeItem{Deployed the app with Streamlit for interactive, real-time data visualization and financial forecasting.}
    \resumeItem{Tech Stack: Python, Streamlit, OpenAI API, Pandas, Numpy, Plotly, News API}
    \resumeItem{Live App: \href{https://aiwrapper.streamlit.app}{AI Wrapper Live App}}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/PriyanshuGupta1102/e-react}{E-Commerce Product Page} \quad $|$ \quad React, Jest, React Testing Library}{July 2025}
\resumeItemListStart
    \resumeItem{Developed a responsive e-commerce interface with an interactive image gallery, user-controlled quantity selectors, and cart management logic using React Hooks.}
    \resumeItem{Authored a comprehensive test suite with Jest and React Testing Library, achieving 90\%+ test coverage to ensure component reliability and prevent UI bugs.}
\resumeItemListEnd

\resumeProjectHeading
{\href{https://github.com/PriyanshuGupta1102/task-api}{Task Management API} \quad $|$ \quad Java, Spring Boot, JUnit, Mockito}{August 2025}
\resumeItemListStart
    \resumeItem{Designed a multi-layered RESTful API for task management using Spring Boot, employing a Repository-Service-Controller pattern to ensure modularity.}
    \resumeItem{Ensured business logic integrity by implementing full CRUD functionality with a 95\% unit test coverage rate using JUnit and Mockito to mock repository layers.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{Languages}: Java, Python, C++, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Frameworks \& Libraries}: Streamlit, Spring Boot, Jest, JUnit, Mockito, React Testing Library}
    \resumeItem{\textbf{Databases \& Tools}: MySQL, Git, Docker, Postman, VS Code, IntelliJ IDEA}
    \resumeItem{\textbf{Methodologies \& Concepts}: API Design (REST), Agile, Quality Assurance, Unit Testing, Integration Testing}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
